Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots

### 2022-05-16 review/response-letter.tex

{\color{blue}

{\hspace*{-4.5em}{[R2:10]}\vspace*{-1.9em}}

Thank you for underlying this possible source of confusion. We have fixed the text to clearly state whether the category is in the former or latter occurrence.

\begin{formal}
  \color{black} [...] there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa. The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the opposite occurs with} lighter-than-air aerial robots (e.g., blimps). [...]
  \vspace*{1ex}
\end{formal}}

### 2022-05-16 energy-planning.tex
fixed Figure 6 with reviewers comments (need to fix refs in text with the figure)

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers provide forward thrust, and control surfaces perform maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa. The {\color{blue}former} occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the latter with} lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
\begin{ctb}
  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
\end{ctb}

@@

>>>>

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers provide forward thrust, and control surfaces perform maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa. The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the opposite occurs with} lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
\begin{ctb}
  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
\end{ctb}

@@

\begin{figure*}
  %\vspace*{-4ex}
  \centering
  \footnotesize
  \input{\figpath/results/new_physics2/new_trajs-ener_I-II.tikz}
  \label{fig:1}
  \caption{.}
  \vspace*{-3ex}
\end{figure*}

\begin{figure*}
  %\vspace*{-4ex}
  \centering
  \footnotesize
  \input{\figpath/results/new_physics2/new_trajs-ener_LOWER_i-ii.tikz}
  \label{fig:2}
  \caption{.}
  \vspace*{-3ex}
\end{figure*}
